{lato}\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=1.5cm,right=10cm,marginparwidth=7.7cm,marginparsep=0.8cm,top=1.25cm,bottom=1.25cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
}

\usepackage[official]{eurosym}


\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%bullets & rating marker
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Sambhab Mishra}
\tagline{<Code + Biology>}
% Add Profile Picture here
% \photo{3.3cm}{profile.jpg}

\personalinfo{
    \homepage{Xtensive.ai}
    \email{Mishrasambhab620@gmail.com}
    \linkedin{https://www.linkedin.com/in/sambhab-mishra-4149431b5/}
    \github{https://github.com/SambhabMishraOfficial}
    
}
\begin{fullwidth}
    \makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\footnotesize}


\marginpar{
    \bigskip%
    \vspace*{
        \dimexpr1pt-\baselineskip
    }
    \raggedright{
        \cvsection{Research}
        \cvevent{\textbf{GiGa Complex}}{}{  May 2023 - Present}{}
        \begin{itemize}
            \item A novel approach to mitigating locust attacks and safeguarding crops involves the application of a ginger and garlic extract mixture, effectively deterring locust infestations by utilizing Allicin from garlic and Diallyl trisulphide from ginger. This concoction acts as an inhibitor of the acetylcholinesterase (AChE) enzyme, inducing neuroexcitation in locusts and preventing crop damage
        \end{itemize}

        \divider

        \cvevent{\textbf{BCDS} - Detecting Urinary Bladder Cancer early}{}{March 2021 - August 2023}{}
        \begin{itemize}
            \item Successfully isolated and characterized the bacteria from the urine sample of the Bladder cancer patients.
            \item The bacteria found in the urine of bladder cancer patient is somehow different from the bacteria found in the urine of a normal human (At genus as well as species level). Analysed using 16s RNA sequencing. Elevation is Firmicutes, Actinobacteria, Bacteroidetes and Proteobacteria (at phyla level). Fusobacterium nucleatum is abundant in BC patient urine.  
        \end{itemize}

        \divider

         \cvevent{\textbf{Bacterial Pigments and their characterization
}}{}{June 2020 - August 2022}{}
        \begin{itemize}
            \item This project was aimed at full characterization of two bacterial pigment i.e. Prodigiosin and Violacein. The pigment prodigiosin was extracted from locally isolated from Serratia marcescens and Violacein was extracted from Chromobacterium violaceum.  Chemical composition characterization using TLC, NMR and GC-MS.The extracted pigment was further checked for different properties including antibacterial, Anticancer, antiparasitic, antifungal, Algicidal, etc.
        \end{itemize}

        \divider

         \cvevent{\textbf{AMar (Aegle Marmelos) Biodegradable planting pots (PATENTED)}}{}{February 2021 - December 2023}{}
        \begin{itemize}
            \item prepared a biodegradable planting pot using coconut coir and epicarp of Aegle marmelos 
            \item This pot attracts the pollinators by its natural fragrance (very helpful for pollination without any artificial ways), eco-friendly, fully biodegradable, cost effective and is based on 14 out of 17 SDG’s.
            \item Provides essential nutrition and minerals to the plants and is durable and flexible.
            \item Patented under the Department of Promotion of Industry and Internal Trade (DPIIT), Ministry of Commerce & Industry, Government of India. Patent application no- 202131043278
        \end{itemize}


        \cvsection{Achievements}
        \begin{itemize}
        \cvitem{{Bal Shakti Puraskar Recipient 2020}}{Jan 2020}{Highest honor bestowed to an Indian below 18 by the \textbf{President of India} at the President's House.}

        \end{itemize}

    }
}

\cvsection{Education}

\cvevent{Bachelors in Biological Sciences (BSc)}{University Of Sheffield}{September 2024 - 2027}{}
\begin{itemize}
    \item To pursue a Bachelors degree in Biological Sciences.
    \item With a special focus on Genetics and Molecular Biology ( With an intergration with Computational Biology )
    \item Qualitative research and In-depth analysis 
\end{itemize}
\divider

\cvevent{High School Dimploma}{Lajpat Rai D.A.V Public School, Cuttcak}{April 2016 - May 2023}{}
\begin{itemize}
    \item 10th Grade:A+
    \item 12th Grade:A+
    \item Subjects: English, Math, Biology, Physics, Chemistry, History, Geography, Economics, Political Science and Computer Science.
\end{itemize}

\cvsection{Experience}
\cvevent{Founder and CEO}{Xtensive.ai}{May 2021 - June 2022}{}
\begin{itemize}
    \item {Revolutionizing the landscape of scientific inquiry, our innovative platform endeavors to empower researchers through the provision of a sophisticated array of AI-driven tools and resources, aimed at augmenting their analytical capabilities and catalyzing transformative discoveries.}
\end{itemize}
\divider

\clearpage
% Anything that I add after this page goes to the next page
\end{document}College London